\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-23 paper/paper.tex
Fix notation of priors, add to computation section.

\begin{enumerate}
\item This model constrains all drive-models to the same failure distribution. For this ``reduced" model we assume the same priors as in Example 1.

\item We allow $t_{pg}$ to vary by drive-model. To help with model identifiably, we tighten the priors on the defective mode:
$$ \mbox{logit}^{-1}\pi \sim \op{Normal}(-3,1),\quad \sigma_1 \sim \op{Lognormal}(0, 1), \quad t_{p1} \sim \op{Normal}(7,2),$$
implying now a prior $90\%$ probability that $\sigma_1$ is between $0.19$ and $5.18$ and $t_{0.5,1}$ between $3.7$ and $10.3$, which, translating from the log-scale, is equivalent to an interval from 1.5 days to 3.4 years.

\item $\sigma_{g2}$ is allowed to vary. Priors for constrained parameters are the same as for model 2.

\item $\pi_g$ varies. Priors for constrained parameters are the same as for model 2.

\end{enumerate}

For the scale hyper-parameters we follow the recommendations of \citet{gelman2014bayesian} and use half-Cauchy priors. As for the location hyper-parameters, we select weakly informative priors consistent with our prior information on hard-drives. The prior for $\eta_\pi$ puts 95\% of prior mass on the interval $(0.006, 0.27)$ for the median proportion defective (What justification? Should maybe be lower.) For $\eta_{\sigma, 2}$, $95\%$ of prior mass is on values greater than $0.037$. Since $\sigma_d$ is the reciprocal of the Weibull shape parameter, this corresponds roughly to an assumption that the median Weibull shape parameter is less than $1/0.037 = 27$. The prior for $\eta_{t_{p_2},2}$ implies that the median 20th percentile for non-defective units is less than greater than 3 days and less than 24 years.

\begin{align*}
  \eta_{\pi} & \sim \op{Normal}(-3, 1)\\
  \tau_{\pi} & \sim \op{Cauchy}^+(0, 1)\\
  \eta_{\sigma ,2} & \sim \op{Normal}(0, 2)\\
  \tau_{\sigma ,2} & \sim \op{Cauchy}^+(0, 1)\\
  \eta_{t_{.2_2},2} & \sim \op{Normal}(9, 2)\\
  \tau_{t_{.2_2},2} & \sim \op{Cauchy}^+(0, 1)
 \end{align*}

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. HMC jointly updates all model parameters by simulating energy preserving paths with random initial momentums along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1,2 and 3 and 16 chains were run for Model 4. The Gelman-Rubin potential scale reduction factors, ``R-hat", which test for lack of convergence by comparing the between versus within chain variability were used. Upon convergence, R-hat converges to 1. For the four model fits, the  maximum values over all the model parameters were 1.005, 1.028, 1.009 and 1.004, respectively. The minimum estimated effective sample size over all the model parameters for the four model fits were 567, 205, 672 and 3330, respectively. No divergent transitions occurred after warmup.

>>>>

\paragraph{Model 1.} Constrain all drive-models to the same GLFP distribution. For this ``reduced" model we assume the same priors as in Example 1.

\paragraph{Model 2.} $t_{p,g}$ varies by drive-model. To help with model identifiably, we tighten the priors on the infant mortality failure mode:
$$ \pi \sim \op{Logit-normal}\langle 7.0\times 10^{-3},\, 2.6 \times 10^{-1} \rangle,$$
$$\sigma_1 \sim \op{Log-normal}\langle 1.4 \times 10^{-1},\, 7.1\rangle,$$ 
$$t_{p1} \sim \op{Log-normal} \langle 2.2 \times 10^1,\, 5.5 \times 10^{4} \rangle.$$

\paragraph{Model 3.} $t_{p,g}$ and $\sigma_{g2}$ vary by drive-model. Priors for constrained parameters are the same as for model 2.

\paragraph{Model 4.} $\pi_g$, $t_{p,g}$ and $\sigma_{g2}$ vary by drive-model. Priors for constrained parameters are the same as for model 2.

Where applicable prior distributions on hyperparameters are as listed below. We follow the recommendation of \citet{gelman2014bayesian} to use half-Cauchy priors on hierarchical scale parameters. As for the location hyperparameters, we choose weakly informative prior distributions centered around the corresponding prior mean for the non-hierarchical model.
% The prior for $\eta_\pi$ puts 95\% of prior mass on the interval $(0.006, 0.27)$ for the median proportion defective (What justification? Should maybe be lower.) For $\eta_{\sigma, 2}$, $95\%$ of prior mass is on values greater than $0.037$. Since $\sigma_d$ is the reciprocal of the Weibull shape parameter, this corresponds roughly to an assumption that the median Weibull shape parameter is less than $1/0.037 = 27$. The prior for $\eta_{t_{p_2},2}$ implies that the median 20th percentile for non-defective units is less than greater than 3 days and less than 24 years.

\begin{align*}
  \eta_{\pi} & \sim \op{Normal}(-3, 1)\\
  \tau_{\pi} & \sim \op{Half-Cauchy}(0, 1)\\
  \eta_{\sigma ,2} & \sim \op{Normal}(0, 2)\\
  \tau_{\sigma ,2} & \sim \op{Half-Cauchy}(0, 1)\\
  \eta_{t_{.2_2},2} & \sim \op{Normal}(9, 2)\\
  \tau_{t_{.2_2},2} & \sim \op{Half-Cauchy}(0, 1).
 \end{align*}

\subsection{Computation}
\label{sec:Computation}
Each model was fit using the {\tt
  rstan}\cite{rstan} package in {\tt R} \cite{r}, which implements a variant of Hamiltonian Monte Carlo (HMC)
\cite{betancourt}. HMC jointly updates all model parameters by simulating energy preserving paths with random initial momentums along the posterior density. This is done to reduce autocorrelation and efficiently explore the posterior. Multiple chains were run for 1500 iterations after 1500 warmup iterations: 4 chains were run for Models 1,2 and 3 and 16 chains were run for Model 4. The Gelman-Rubin potential scale reduction factors, ``R-hat", which test for lack of convergence by comparing the between versus within chain variability were used. Upon convergence, R-hat converges to 1. For the four model fits, the  maximum values over all 140 model parameters were 1.005, 1.028, 1.009 and 1.004, respectively. The minimum estimated effective sample size over the model parameters were 567, 205, 672 and 3330 for Models 1 through 4, respectively. No divergent transitions occurred after warmup.
